---
title: "Results_figures"
author: Kristoffer Wild
date: "`r Sys.Date()`"
output: 
  word_document:
    reference_docx: template.docx
editor_options: 
  chunk_output_type: console
---

``````{r setup, include=FALSE, eval = T, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
options(digits = 3)
rm(list=ls())
sessionInfo()
# Packages
pacman::p_load("dplyr", "car", "ggplot2", "ggdist", "performance", "magick", "cowplot","broom", "emmeans" ,"kableExtra","flextable")
```

# Results
```{r tick results, echo = FALSE, include = FALSE}
tick_data <- read.csv("Data/Ticks_data_final.csv")
####
# sample sizes and Yate's chi square analysis
####
# totals
n_total <- tick_data %>% 
  summarise(n = n())
n_sex <- tick_data %>%
  group_by(Sex) %>% 
  summarise(total = n())
# TICK - by sex
n_tick_sex <- tick_data %>% 
  group_by(Sex, Ticks_Y_N) %>% 
  summarise(count = n())

# TICK percent - by sex
percentage_df <- left_join(n_tick_sex, n_sex, by = "Sex")
percentage_sex <- percentage_df %>%
  mutate(percentage = count / total * 100) %>% 
  mutate_if(is.numeric, round, 0)
# TEST chi square
sex_yates <- readRDS(file = "Models/sex_yates.rds") 
sex_yates_tbl <- tidy(sex_yates) %>%
  mutate(n = n_total$n) 


####
# Logistic regression SVL and tick presence 
####
logit_male_model <- readRDS(file = "Models/logit_male_model.RDS")%>% 
  tidy() 


####
# Sprint speed results: 25CM & 2M
####
# model - sprint 25
sprint_25CM <- readRDS(file = "Models/sprint_25CM.rds")
sprint_25CM_summary <- summary(sprint_25CM)
# LS mean - sprint 25
sprint_25CM_LS <- emmeans(sprint_25CM, pairwise ~ Ticks_Y_N) 
sprint_25CM_LS_emmean <- as.data.frame(sprint_25CM_LS$emmeans)
sprint_25CM_LS_contrast <- as.data.frame(sprint_25CM_LS$contrasts)

# model - sprint_2M
sprint_2M <- readRDS(file = "Models/sprint_2M.rds")
sprint_2M_summary <- summary(sprint_2M)
# LS mean - sprint 25
sprint_2M_LS <- emmeans(sprint_2M, pairwise ~ Ticks_Y_N) 
sprint_2M_LS_emmean <- as.data.frame(sprint_2M_LS$emmeans)
sprint_2M_LS_contrast <- as.data.frame(sprint_2M_LS$contrasts)


########
# body condition
########
bci_mod <- readRDS(file = "Models/BCI_ticks.rds")
bci_mod_summary <- as.data.frame(anova(bci_mod))

```
*3.1 | Results*
<p>A total of `r n_total[1,1]` lizards were captured (females n= `r n_sex[1,2]`; males `r n_sex[2,2]`) during the 2014 and 2015 field seasons. The frequency of tick infections was highly sex-specific, with the frequency of tick infection being over 2 times higher in males (n = `r percentage_sex[4,3]`; `r percentage_sex[4,5]`%) than in females (n = `r percentage_sex[2,3]`; `r percentage_sex[2,5]`%). Females were therefore precluded from further statistical analysis because the difference in tick infections was significantly different between sex (x$^2$ = `r sex_yates_tbl[1,1]`; df = `r sex_yates_tbl[1,3]`; n = `r sex_yates_tbl[1,5]`; p = `r sex_yates_tbl[1,2]`). Infection rate for males ranged one to seven ticks per individual. There was a positive relationship between male body size, and the number of ticks (F$_{1,51}$ = `r logit_male_model[2,2]`, p = `r logit_male_model[2,5]`), where larger males had a higher probability of tick infection than smaller males (Fig. 1). Maximum sprint speed was significantly higher in uninfected lizards (LS mean = `r sprint_25CM_LS_emmean[1,2]`m/sec) in comparison to infected lizards (LS mean = `r sprint_25CM_LS_emmean[2,2]`m/sec; F$_{2,51}$ = 16.12; p = `r sprint_25CM_LS_contrast[1,6]`; Fig. 2a). Maximum 2-meter run speed was significantly higher in uninfected lizards (LS mean = `r sprint_2M_LS_emmean[1,2]`m/sec) than in infected lizards (LS mean = `r sprint_2M_LS_emmean[2,2]`m/sec; F$_{2,51}$ = 15.01; p = `r sprint_2M_LS_contrast[1,6]`; Fig. 2b). There were no differences in body condition indices between uninfected and infected lizards (F$_{2,51}$ = 0.025; p = `r bci_mod_summary[1,5]`). <p>


\newpage
```{r Fig1,echo= FALSE}
########
# Logistic regression for presence/abcense and body size in males
########
tick_data <- read.csv(file = "Data/Ticks_data_final.csv")
logit_male_dat <- tick_data %>% 
  filter(Sex == "M")

# Logistic regression: model summary 
logit_male_model<- glm(Ticks_1Y_0N ~ SVL, data=logit_male_dat, family=binomial(link="logit"))

# Logistic regression: create a new data frame for predictions
newdata <- data.frame(SVL = seq(min(logit_male_dat$SVL), 
                                max(logit_male_dat$SVL), 
                                length.out = 100))

# Logistic regression: compute the fitted lines and SE's
predicitions <-predict(logit_male_model,
                       newdata = newdata,
                       type = "link",
                       se.fit = TRUE) %>% 
  data.frame() %>% 
  mutate(ll = fit - 1.96 * se.fit,
         ul = fit + 1.96 * se.fit) %>% 
  select(-residual.scale, -se.fit) %>% 
  mutate_all(plogis) %>%
  bind_cols(newdata)

# Logistic regression: plotting model
logistic_regression_males <- predicitions %>% 
  ggplot(aes(x = SVL)) +
  geom_ribbon(aes(ymin = ll, ymax = ul),
              alpha = 1/2) +
  geom_line(aes(y = fit)) +
  stat_dots(data = logit_male_dat %>% 
              mutate(Ticks = factor(Ticks_1Y_0N, 
                                    levels = c("Yes", "No"))),
            aes(y = Ticks_1Y_0N, 
                side = ifelse(Ticks_1Y_0N == 0, "top", "bottom"),
                color = Ticks_Y_N),
            scale = 0.07, shape = 19) +
  scale_color_manual("Tick Presence", values = c("grey", "#D55E00")) +
  scale_x_continuous("SVL (cm)") +
  scale_y_continuous("probability of infection",
                     expand = c(0, 0)) +
  theme_bw() +
  theme(strip.text = element_text(face = "bold"),
        legend.position = "none")


# bring Legend image
Tick_image <- magick::image_read("Final_figures/Legend_LR.png") %>% 
  magick::image_background("none")
image <- image_fill(Tick_image, 'none')
tick_raster <- as.raster(image)

# Regression final plot
Regression_final <- ggdraw() +
  draw_plot(logistic_regression_males) +
  draw_image(tick_raster, scale = .185, x = -.32, y= 0.38)

#save this figure in the correct folder and bring in to knit
knitr::include_graphics("Final_figures/Figure_1.pdf")
```
Figure 1. 

\newpage
```{r Fig2,echo= FALSE}
tick_data <- read.csv(file = "Data/Ticks_data_final.csv")
sprint_25cm_data <- tick_data %>% 
  filter(Sex == "M") %>% 
  select(HLL, Mass, SVL, Ticks_Y_N, Max_25cm)

# model
sprint_25cm_mod <- lm(Max_25cm ~ HLL + Ticks_Y_N, data=sprint_25cm_data)

# plot
sprint_25cm_plot <- ggplot(sprint_25cm_mod, 
                           aes(x=HLL, y=Max_25cm, 
                               color=Ticks_Y_N, shape=Ticks_Y_N)) +
  geom_point() +
  stat_smooth(method=lm, alpha = .22) +
  scale_color_manual("Tick Presence", values = c("grey", "#D55E00")) +
  scale_shape_manual("Tick Presence", values = c(16, 17)) +
  scale_y_continuous(limits=c(1.3,4.01), breaks = seq(1.5, 4, by = .5)) +
  ylab(expression("Speed"~(~ms^{"-1"}))) +
  xlab("hind limb length (mm)") + 
  annotate("text", x = 35, y = 4.0, label = "Maximum sprint speed", fontface = "bold", size = 5)+
  theme_bw() +
  theme(strip.text = element_text(face = "bold"),
        legend.position = "none")

# bring Legend image
Tick_image <- magick::image_read("Final_figures/Treatment_leg.png") %>% 
  magick::image_background("none")
image <- image_fill(Tick_image, 'none')
tick_raster <- as.raster(image)

# 25CM final plot
Sprint_25cm_final <- ggdraw() +
  draw_plot(sprint_25cm_plot) +
  draw_image(tick_raster, scale = .185, x = -.32, y= 0.38) 



########
# ANCOVA : 2m sprint speed 
# MALES
########
sprint_2m_data <- tick_data %>% 
  filter(Sex == "M") %>% 
  select(HLL, Mass, SVL, Ticks_Y_N, Max_2m)

# model
sprint_2m_mod <- lm(Max_2m ~ HLL + Ticks_Y_N, data=sprint_2m_data)

# plot
sprint_2m_plot <- ggplot(sprint_2m_mod, 
                           aes(x=HLL, y=Max_2m, 
                               color=Ticks_Y_N, shape=Ticks_Y_N)) +
  geom_point() +
  stat_smooth(method=lm, alpha = .22) +
  scale_color_manual("Tick Presence", values = c("grey", "#D55E00")) +
  scale_shape_manual("Tick Presence", values = c(16, 17)) +
  scale_y_continuous(limits=c(.3,3), breaks = seq(.5, 3, by = .5)) +
  ylab(expression("Speed"~(~ms^{"-1"}))) +
  xlab("hind limb length (mm)") + 
  annotate("text", x = 33.3, y = 3.0, label = "2 Meter run", fontface = "bold", size = 5)+
  theme_bw() +
  theme(strip.text = element_text(face = "bold"),
        legend.position = "none")

# add legend
Sprint_2m_final <- ggdraw() +
  draw_plot(sprint_2m_plot) +
  draw_image(tick_raster, scale = .185, x = -.32, y= 0.38) 

# final plot with both
Final_sprint <- plot_grid(Sprint_25cm_final, Sprint_2m_final, labels = c('A', 'B'))

#save this figure in the correct folder and bring in to knit
knitr::include_graphics("Final_figures/Figure_2.pdf")
```
